\documentclass[12pt, titlepage]{article}

\usepackage{tabularx}
\usepackage{longtable}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{xr}
\usepackage{siunitx}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{hyperref}
\usepackage[numbib,nottoc]{tocbibind}
\hypersetup{
    colorlinks,
    citecolor=green,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}
\usepackage{enumitem}

\usepackage{xr}
\externaldocument[SRS-]{../../SRS/glassbr_srs}
\newcommand{\rref}[1]{R\ref{#1}}

\newcounter{testnum} %Assumption Number
\newcommand{\tcthetestnum}{TC\thetestnum}
\newcommand{\tcref}[1]{TC\ref{#1}}

\input{../../Comments}

\newcommand{\progname}{GlassBR}

\begin{document}

\title{Glass Breakage Analysis: System Verification and Validation Plan for \progname{}
  \wss{Include the name GlassBR here}\aida{Fixed}} 
\author{Vajiheh Motamer}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
10/26/18 & 1.0 & Initial Draft\\
12/21/18 & 1.1 & Updates based on Dr.~Smith's feedback\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}
The symbols, abbreviations, and acronyms used in this document include those 
defined in the table below, as well as any defined in the tables found in 
Section \ref{SRS-sec_abbrev} of the Software Requirements Specification (SRS) 
document.
\newline

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
    TC & Test Case\\
  VnV & Verification and Validation\\
  MIS & Module Interface Specification\\
  MG & Module Guide\\
  \bottomrule
\end{tabular}\\

\newpage

\tableofcontents

\listoftables

\newpage

\pagenumbering{arabic}

\noindent This document presents the system verification and validation plan 
for the software. General information regarding the system under test and the 
objectives of the verification and validation activities is provided in Section 
\ref{sec_GenInfo}. Overviews of verification plans for the SRS, design, and 
implementation are given in Section \ref{sec_Plan}, along with a summary of the 
validation plan for the software. Section \ref{sec_System} details specific  
system test cases for verifying the requirements outlined in Section 
\ref{SRS-sec_Reqs} of the SRS. A summary of planned static verification 
activities can be found in Section \ref{sec_Static} of this document.

\section{General Information} \label{sec_GenInfo}

\subsection{Summary}

\noindent The software being tested is the Glass Breakage Analysis Program 
(\progname{}). Based on user-defined glass type and blast properties,
\progname{} interprets the inputs to give out the outputs which
predict whether the glass slab can withstand the blast under the given conditions. The blast under
consideration is a type of  blast load. Software is helpful to efficiently and correctly
predict the blast risk involved with the glass slab using an intuitive interface.

\subsection{Objectives}

\noindent The purpose of the verification and validation activities is to 
confirm that \progname{} exhibits desired software qualities. The primary 
objective is to build confidence in the correctness of the software. The tests 
described in this document cannot definitively prove correctness, but they can 
build confidence by verifying that the software is correct for the cases 
covered by tests. Other important qualities to be verified are the 
portability and reusability of the software.

\subsection{Relevant Documentation}

\noindent Extensive information about the purpose and requirements of
\progname{} can be found in the SRS document. This System VnV Plan is
complemented by the System VnV Report, where the results of the tests planned in
this document are discussed. For more details on test cases specific to the
implementation of \progname{}, consult the Unit VnV Plan document. The latest
documentation for \progname{} can be found on GitHub, at \newline
\href{https://github.com/smiths/caseStudies/tree/master/CaseStudies/glass}
{https://github.com/smiths/caseStudies/tree/master/CaseStudies/glass}. \wss{Good!}\aida{Thanks! I have fixed it throughout the document.}

\section{Plan} \label{sec_Plan}
	
\subsection{Verification and Validation Team}

\noindent Responsible member for the verification and validation 
of \progname{} is Vajiheh Motamer.

\subsection{SRS Verification Plan}

\noindent The SRS for the project will be reviewed by Dr. Smith and some of the class mates in CAS741.
So, feedback will be provided. Some SRS feedback for this project have been
provided and addressed using github issue tracker. Besides, during preparing of all steps SRS will be reviewed and if would be required, the changes would be made.

\subsection{Design Verification Plan}

\noindent The design of \progname{} 's  documents will be verified by getting feedback from Dr.
Spencer Smith and my CAS 741 classmates : Malavika Srinivasan
 for the MG and Robert White
 for the MIS. The Module Guide and Module Interface Specification will
contain information about the software design. Feedback is expected to be
provided by reviewers via github issue tracker. \wss{You can be more descriptive
  here, since you know the names of who is going to review each of your
  documents (through Repos.xlsx)}\aida{Fixed.}

\subsection{Implementation Verification Plan} \label{sec_ImpPlan}

The implementation of the \progname{} program will be verified by performing
statically code review with Dr.\ Smith \wss{\LaTeX{} has a rule that it
  inserts two spaces at the end of a sentence.  It detects a sentence as a
  period followed by a capital letter.  This comes up, for instance, with
  Dr. Smith.  Since the period after Dr.\ isn't actually the end of a sentence,
  you need to tell \LaTeX{} to insert one space.  You do this either by Dr.\
  Smith (if you don't mind a line-break between Dr.\ and Smith), or Dr.~Spencer
  Smith (to force \LaTeX{} to not insert a line break).}\aida{Fixed}  and the classmates in
CAS741 and dynamically by executing the test cases detailed in this plan and the
unit VnV plan using Python \wss{spell check!}\aida{Fixed} testing frameworks.

\subsection{Software Validation Plan}

There is no validation plan for \progname{} because there is not any external validation source.\wss{You should the reason why
  there is no software validation plan.} \aida{Done}

\section{System Test Description} \label{sec_System}

System testing for the \progname{} ensures that the correct inputs produce
the correct outputs. The test cases in this section are derived from the
instance models and the requirements detailed in the tool’s SRS. These values were 
taken from the test input files for \progname{} which can be found on GitHub, at 
\href{https://github.com/smiths/caseStudies/tree/master/CaseStudies/glass}
{https://github.com/smiths/caseStudies/tree/master/CaseStudies/glass}. \wss{proof read!}\aida{Done}. Individual 
test cases will reference the table as input in Table~\ref{defaultInputTBL} but specify new values for any 
input parameter that should have a different value than specified by the table.

\subsection{Tests for Functional Requirements}

\subsubsection{User Input Tests}

\paragraph{Valid User Input}

~\newline \noindent The following set of test cases is intended to cover 
different forms of valid user input. These values were 
taken from the test input files for \progname{} can be found on GitHub, at 
\href{https://github.com/smiths/caseStudies/tree/master/CaseStudies/glass/src}
{https://github.com/smiths/caseStudies/tree/master/CaseStudies/glass/src}.  \wss{You should say where the values in
  Table 1 come from.} \aida{I 'm going to move test cases in the ``src'' to the test folder, so if you approve, I will do. So, maybe it would be better to reference to exact path of the project. would'nt it?}

\begin{enumerate}[label=TC\arabic*:,ref={\arabic*}]
%BeginTestCase1
\item [TC\refstepcounter{testnum}\thetestnum: \label{TC_defultInput}] 
Tst\_Pb\_DefaultValues

Control: Automatic
					
Initial State: New session
					
Input: As described in Table~\ref{defaultInputTBL}.
					
Output: \\
$\hspace*{2cm} P_b= (1.301524590203718e-04) < P_{b_{\text{tol}}}$ ,\\
$\hspace*{2cm} Demand (q) = (3.258285992018616e+00) ,\\
$\hspace*{2cm} $Capacity (LR)=(6.843002155788037e+00) > q$, \\
$\hspace*{2cm}$\text{$\text{is\_safePb} = \text{True}$ and $\text{is\_safeLR} =
  \text{True}$, The glass is considered safe.}  \wss{Where did these expected
  values come from?  You should tell the reader so that they can judge whether
  these values make sense.} \aida{it has described in the test case derivation.}  \wss{You don't need brackets around your numbers.}
\wss{For scientific notation, you don't use the $e$ notation in \LaTeX{}, you
  can write the multiplication and the power of $10$ explicitly.  For instance,
  $P_b= 1.301524590203718 \times 10^{-4}$}

How test will be performed: Unit testing using PyUnit.

Test Case Derivation: These expected values has been derived using of equations from Risk of Failure (B) from DD\ref{SRS-DD_B} and ``Probability of Glass Breakage'' from DD\ref{SRS-DD_prob} based on the input values in the Table~\ref{defaultInputTBL}.

\begin{table}[!h]
\centering

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ | p{3cm} | p{3cm}| p{3cm} | }  
\toprule
\textbf{Input} & \textbf{Value} & \textbf{Unit}\\
\midrule 
		$\text{a}$ &1600 & \text{m} \\
		$\text{b}$ &1500 & \text{m}\\
		$\text{g}$ &\text{HS} & \text{-}\\
		$P_{b_{\text{tol}}}$ &0.008& \text{-}\\
		$\text{SD}_x$ & 0 &  \si{\meter}\\
		$\text{SD}_y$ &1.5 & \si{\metre}\\
		$\text{SD}_z$ & 11.0 &\si{\metre}\\
		$\text{t}$ &10.0 & \text{mm}\\
		$\text{TNT}$ &1.0 & \text{-}\\
                $w$ &10.0	& \si{\kilo\gram}\\
		\bottomrule
\end{tabular}
\caption{Inputs for Tst\_Pb\_DefaultValues} 
\label{defaultInputTBL}
\end{table}

%EndTestCase1
\wss{You don't normally need to hard code in newpages}\aida{Thanks! Done throughout the document.}

%BeginTestCase2				
\item [TC\refstepcounter{testnum}\thetestnum: \label{TC_SmallDimensionInput}] 
Tst\_ Pb\_ SmallDimensionValues \wss{I don't understand how the dimensions are
  small values.  They look like regular values.} \aida{It has been considered smaller than dimentions in the table 1. Besides, I have taken these values from TestingPythonGlassBR.pdf in the path of project that it has referenced to testinput1.txt for small dimentions as input file. }

Control: Automatic
					
Initial State: New session
					
Input: As described in Table~\ref{SmallDimensionTBL}.
					
Output: \\
$\hspace*{2cm} P_b= (1.824662149424894e-03) < P_{b_{\text{tol}}}$,\\
$\hspace*{2cm} Demand (q) = (3.658003449421614e+00) ,\\
$\hspace*{2cm} $Capacity (LR)=(4.916016610996773e+00) > q$, \\
$\hspace*{2cm}$\text{$\text{is\_safePb} = \text{True}$ and $\text{is\_safeLR} = \text{True}$, The glass is considered safe.}



How test will be performed: Unit testing using PyUnit.

Test Case Derivation:  \ref{SRS-IM_prob} and \ref{SRS-T_Pb} in SRS.



\begin{table}[!h]
\centering

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ | p{3cm} | p{3cm}| p{3cm} | }  
\toprule
\textbf{Input} & \textbf{Value} & \textbf{Unit}\\
\midrule 
		$\text{a}$ &1200 & \text{m} \\
		$\text{b}$ &1000 & \text{m}\\
		$\text{g}$ &\text{AN} & \text{-}\\
		$P_{b_{\text{tol}}}$ &0.010& \text{-}\\
		$\text{SD}_x$ & 0 &  \si{\meter}\\
		$\text{SD}_y$ &2.0& \si{\metre}\\
		$\text{SD}_z$ & 10.0 &\si{\metre}\\
		$\text{t}$ &8.0 & \text{mm}\\
		$\text{TNT}$ &1.0 & \text{-}\\
$w$ &10.0	& \si{\kilo\gram}\\
		\bottomrule
\end{tabular}
\caption{Inputs for Tst\_ Pb\_ SmallDimensionValues} 
\label{SmallDimensionTBL}
\end{table}


%EndTestCase2
\newpage
%BeginTestCase3

\item [TC\refstepcounter{testnum}\thetestnum: \label{TC_LargeDimensionInput}] 
Tst\_Pb\_LargeDimensionValues

Control: Automatic
					
Initial State: New session
					
Input: As described in Table~\ref{LargeDimensionTBL}.
					
Output: \\
$\hspace*{2cm} P_b= (3.459068155453604e-04) < P_{b_{\text{tol}}}$,\\
$\hspace*{2cm} Demand (q) = (5.777809021268771e+00) ,\\
$\hspace*{2cm} $Capacity (LR)=(1.092974208994522e+01) > q$ ,\\
$\hspace*{2cm}$\text{$\text{is\_safePb} = \text{True}$ and $\text{is\_safeLR} = \text{True}$, The glass is considered safe.}




How test will be performed: Unit testing using PyUnit.

Test Case Derivation:  \ref{SRS-IM_prob} and \ref{SRS-T_Pb} in SRS.


\begin{table}[!h]
\centering

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ | p{3cm} | p{3cm}| p{3cm} | }  
\toprule
\textbf{Input} & \textbf{Value} & \textbf{Unit}\\
\midrule 
		$\text{a}$ &1600 & \text{m} \\
		$\text{b}$ &1500 & \text{m}\\
		$\text{g}$ &\text{HS} & \text{-}\\
		$P_{b_{\text{tol}}}$ &0.010& \text{-}\\
		$\text{SD}_x$ & 0 &  \si{\meter}\\
		$\text{SD}_y$ &1.5& \si{\metre}\\
		$\text{SD}_z$ & 11.0 &\si{\metre}\\
		$\text{t}$ &10.0 & \text{mm}\\
		$\text{TNT}$ &1.0 & \text{-}\\
$w$ &10.0	& \si{\kilo\gram}\\
		\bottomrule
\end{tabular}
\caption{Inputs for Tst\_ Pb\_ LargeDimensionValues} 
\label{LargeDimensionTBL}
\end{table}
%EndTestCase3
\newpage
%BeginTestCase4
\item [TC\refstepcounter{testnum}\thetestnum: \label{TC_LowPbTol}] 
Tst\_ Pb\_ LowPbTol

Control: Automatic
					
Initial State: New session
					
Input: As described in Table~\ref{LowPbTolTBL}.
					
Output: \\
$\hspace*{2cm} P_b= (1.301524590203718e-04) > P_{b_{\text{tol}}}$,\\
$\hspace*{2cm} Demand (q) = (3.258285992018616e+00) ,\\
$\hspace*{2cm} $Capacity (LR)=(3.124424950223241e+00) \ngtr q$ ,\\
$\hspace*{2cm}$\text{$\text{is\_safePb} = \text{False}$ and $\text{is\_safeLR} = \text{False}$, The glass is NOT considered safe.}



How test will be performed: Unit testing using PyUnit.

Test Case Derivation:  \ref{SRS-IM_prob} and \ref{SRS-T_Pb} in SRS.


\begin{table}[!h]
\centering

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ | p{3cm} | p{3cm}| p{3cm} | }  
\toprule
\textbf{Input} & \textbf{Value} & \textbf{Unit}\\
\midrule 
		$\text{a}$ &1600 & \text{m} \\
		$\text{b}$ &1500 & \text{m}\\
		$\text{g}$ &\text{HS} & \text{-}\\
		$P_{b_{\text{tol}}}$ &0.008& \text{-}\\
		$\text{SD}_x$ & 0 &  \si{\meter}\\
		$\text{SD}_y$ &2.5& \si{\metre}\\
		$\text{SD}_z$ & 6.0 &\si{\metre}\\
		$\text{t}$ &10.0 & \text{mm}\\
		$\text{TNT}$ &1.0 & \text{-}\\
$w$ &10.0	& \si{\kilo\gram}\\
		\bottomrule
\end{tabular}
\caption{Inputs for Tst\_ Pb\_ LowPbTol} 
\label{LowPbTolTBL}
\end{table}

%EndTestCase4
\newpage
%BeginTestCase5
\item [TC\refstepcounter{testnum}\thetestnum: \label{TC_DiffSDInput}] 
Tst\_ Pb\_ DiffSDValues

Control: Automatic
					
Initial State: New session
					
Input: As described in Table~\ref{DiffSDTBL}.
					
Output: \\
$\hspace*{2cm} P_b= (1.185574651484522e-02) >  P_{b_{\text{tol}}}$, \\
$\hspace*{2cm} Demand (q) = (7.377747177423622e+00) ,\\
$\hspace*{2cm} $Capacity (LR)=(6.843002155788037e+00) \ngtr q$ ,\\
$\hspace*{2cm}$\text{$\text{is\_safePb} = \text{False}$ and $\text{is\_safeLR} = \text{False}$, The glass is NOT considered safe.}


How test will be performed: Unit testing using PyUnit.

Test Case Derivation:  \ref{SRS-IM_prob} and \ref{SRS-T_Pb} in SRS.


\begin{table}[!h]
\centering

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ | p{3cm} | p{3cm}| p{3cm} | }  
\toprule
\textbf{Input} & \textbf{Value} & \textbf{Unit}\\
\midrule 
		$\text{a}$ &1600 & \text{m} \\
		$\text{b}$ &1500 & \text{m}\\
		$\text{g}$ &\text{HS} & \text{-}\\
		$P_{b_{\text{tol}}}$ &0.008& \text{-}\\
		$\text{SD}_x$ & 0.0 &  \si{\meter}\\
		$\text{SD}_y$ &2.5& \si{\metre}\\
		$\text{SD}_z$ & 6.0 &\si{\metre}\\
		$\text{t}$ &0.008 & \text{mm}\\
		$\text{TNT}$ &1.0 & \text{-}\\
$w$ &10.0	& \si{\kilo\gram}\\
		\bottomrule
\end{tabular}
\caption{Inputs for Tst\_ Pb\_ DiffSDValues} 
\label{DiffSDTBL}
\end{table}

%EndTestCase5
\newpage
%BeginTestCase6

\item [TC\refstepcounter{testnum}\thetestnum: \label{TC_HighChgWght}] 
Tst\_ Pb\_ HighChgWght

Control: Automatic
					
Initial State: New session
					
Input: As described in Table~\ref{HighChgWghtTBL}.
					
Output: \\
$\hspace*{2cm} P_b= (2.497577817262034e-01) >  P_{b_{\text{tol}}}$, \\
$\hspace*{2cm} Demand (q) = (1.428204355548630e+01) ,\\
$\hspace*{2cm} $Capacity (LR)=(6.843002155788037e+00) \ngtr q$, \\
$\hspace*{2cm}$\text{$\text{is\_safePb} = \text{False}$ and $\text{is\_safeLR} = \text{False}$, The glass is NOT considered safe.}


How test will be performed: Unit testing using PyUnit.

Test Case Derivation:  DD\ref{SRS-DD_prob} and IM\ref{SRS-IM_Pb} in SRS.



\begin{table}[!h]
\centering

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ | p{3cm} | p{3cm}| p{3cm} | }  
\toprule
\textbf{Input} & \textbf{Value} & \textbf{Unit}\\
\midrule 
		$\text{a}$ &1600 & \text{m} \\
		$\text{b}$ &1500 & \text{m}\\
		$\text{g}$ &\text{HS} & \text{-}\\
		$P_{b_{\text{tol}}}$ &0.008& \text{-}\\
		$\text{SD}_x$ & 0 &  \si{\meter}\\
		$\text{SD}_y$ &1.5& \si{\metre}\\
		$\text{SD}_z$ & 11.0 &\si{\metre}\\
		$\text{t}$ &10.0 & \text{mm}\\
		$\text{TNT}$ &1.0 & \text{-}\\
$w$ &60.0	& \si{\kilo\gram}\\
		\bottomrule
\end{tabular}
\caption{Inputs for Tst\_ Pb\_ HighChgWght} 
\label{HighChgWghtTBL}
\end{table}

%EndTestCase6
\newpage
%BeginTestCase7

\item [TC\refstepcounter{testnum}\thetestnum: \label{TC_LowThicknessInput}] 
Tst\_ Pb\_ LowThickness

Control: Automatic
					
Initial State: New session
					
Input: As described in Table~\ref{LowThicknessTBL}.
					
Output: \\
$\hspace*{2cm} P_b= (2.528418262282350e-01) >  P_{b_{\text{tol}}}$, \\
$\hspace*{2cm} Demand (q) = (3.258285992018616e+00) ,\\
$\hspace*{2cm} $Capacity (LR)=(1.716982174845693e+00) \ngtr q$, \\
$\hspace*{2cm}$\text{$\text{is\_safePb} = \text{False}$ and $\text{is\_safeLR} = \text{False}$, The glass is NOT considered safe.}


How test will be performed: Unit testing using PyUnit.

Test Case Derivation:  \ref{SRS-IM_prob} and \ref{SRS-T_Pb} in SRS.



\begin{table}[!h]
\centering

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ | p{3cm} | p{3cm}| p{3cm} | }  
\toprule
\textbf{Input} & \textbf{Value} & \textbf{Unit}\\
\midrule 
		$\text{a}$ &1600 & \text{m} \\
		$\text{b}$ &1500 & \text{m}\\
		$\text{g}$ &\text{HS} & \text{-}\\
		$P_{b_{\text{tol}}}$ &0.008& \text{-}\\
		$\text{SD}_x$ & 0 &  \si{\meter}\\
		$\text{SD}_y$ &1.5& \si{\metre}\\
		$\text{SD}_z$ & 11.0 &\si{\metre}\\
		$\text{t}$ &3.0 & \text{mm}\\
		$\text{TNT}$ &1.0 & \text{-}\\
$w$ &10.0	& \si{\kilo\gram}\\
		\bottomrule
\end{tabular}
\caption{Inputs for Tst\_ Pb\_ LowThickness} 
\label{LowThicknessTBL}
\end{table}

\end{enumerate}
%EndTestCase7

\wss{The input and output values for the above test cases do not seem to follow
  a discernible pattern.  Multiple values are modified between tests, but I
  don't know the rationale for the modification.  You would usually hold all
  values constant and then only modify 1 value (or maybe two values, if they are
  related like $a$ and $b$).  This approach is more systematic, and it also
  means you don't have to repeat the entire table every time.  You certainly do
  want test cases where the glass is safe and where it isn't, but you didn't
  distinguish the names of any of your test cases based on this.}\aida{Dr.~Smith I did not make sense of your comment, as you mentioned I held all values constant and only modify one of the values, for example in this case I modified just thickness which is too low and the result is not considered safe. }

\paragraph{Invalid User Input}

~\newline \noindent The test cases described in Table~\ref{testCheckConstraints} 
are intended to cover all invalid input possibilities. Invalid input is input 
that defies the data constraints described in Section 
\ref{SRS-sec_DataConstraints} of the SRS. These test cases are identical to 
each other with the exception of their input. The input for each is specified 
in Table~\ref{testCheckConstraints}. For each test case, the inputs which have not been specified 
in this table, have been specified in Table~\ref{defaultInputTBL}. Besides,The
\wss{proof read} expected output has been specified for each test case and the control method 
for these test cases is automatic. The initial state for each is a new session. 
The tests will be performed as automated tests on the PyUnit.

%Table : testCheckConstraints
\begin{table}[h!]
\centering
\caption{TestCheckConstraints}
\label{testCheckConstraints}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{*{4}{|c|}}
\hline
\textbf{Test Case} & \textbf{Test Name} & \textbf{Significant Input} & \textbf{Expected Output} \\
\hline
\hline
TC\refstepcounter{testnum}\thetestnum \label{TC_checkAPositiveTest}  & checkAPositiveTest  & a = -1600 & InputError: a and b must be greater than 0 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_checkBPositiveTest} & checkBPositiveTest &  b = -1500 & InputError: a and b must be greater than 0 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_checkSmallAspectRTest} & checkSmallAspectRTest & b = 2000 & (a/b=0.8\textless1); InputError: a/b must be between 1 and 5 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_checkLargeAspectRTest} & checkLargeAspectRTest & b = 200 & (a/b=8\textgreater5); InputError: a/b must be between 1 and 5 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_checkValidThicknessTest} & checkValidThicknessTest & t = 7 & InputError: t must be in {[}2.5,2.7,3.0,4.0,5.0,6.0,8.0, 10.0,12.0,16.0,19.0,22.0{]}  
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_checkLowerConstrOnWTest} & checkLowerConstrOnWTest  & w = 3 & InputError: wtnt must be between 4.5 and 910 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_ checkUpperConstrOnWTest} & checkUpperConstrOnWTest & w = 1000 & InputError: wtnt must be between 4.5 and 910 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_checkTNTPositiveTest} & checkTNTPositiveTest & tnt = -2 & InputError: TNT must be greater than 0 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_checkLowerConstrOnSDTest } & checkLowerConstrOnSDTest & sdx = 0; sdy = 1.0; sdz = 2.0 & InputError: SD must be between 6 and 130 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_checkUpperConstrOnSDTest} & checkUpperConstrOnSDTest &  sdx = 0; sdy = 200; sdz = 100 & InputError: SD must be between 6 and 130 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_ incorrectA0Test } & incorrectA0Test & a = 0 & InputError: a and b must be greater than 0 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_ incorrectB0Test} & incorrectB0Test  & b = 0 & InputError: a and b must be greater than 0 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_ incorrectTNT0Test} & incorrectTNT0Test & tnt = 0 & InputError: TNT must be greater than 0 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_incorrectAspectREqLwrBndTest } & incorrectAspectREqLwrBndTest & a = 1500; b = 1500 & (a/b = 1);  ``a/b must be between 1 and 5, equation would be uncertaint.'' 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_ incorrectAspectREqUpprBndTest} & incorrectAspectREqUpprBndTest & a = 7500; b = 1500 & (a/b = 5); ``a/b must be between 1 and 5, equation would be uncertaint.''
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_ incorrectWEqLwrBndTest } & incorrectWEqLwrBndTest & w = 4.5 & "wtnt must be greater than or equal \textit{Wmin} = 4.5, equation would be uncertaint." 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_ incorrectWEqUpprBndTest} & incorrectWEqUpprBndTest & w = 910 & "wtnt must be less than or equal \textit{Wmax} = 910, equation would be uncertaint." 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_ incorrectSDEqLwrBndTest} & incorrectSDEqLwrBndTest & sdx = 0; sdy = 6; sdz = 0 & ``SD must be greater than or equal \textit{SDmin} =  6, equation would be uncertaint.'' 
\\
TC\refstepcounter{testnum}\thetestnum \label{TC_incorrectWEqUpprBndTest} & incorrectSDEqUpprBndTest  & sdx = 130; sdy = 0; sdz = 0 & ``SD must be greater than or equal \textit{SDmax} =  130, equation would be uncertaint.'' 
\\
\hline
\end{tabular}
\end{adjustbox}
\end{table}

\wss{The error messages for the last test cases are all the same ``Encountered
  an unexpected exception''.  Is this what the SRS says?  We really could have a
  more descriptive error message, as for the other cases.} \aida{Although wtnn and SD equation in the UpperBand and Lowerband has been considered in the SRS as valid value, however it throw an error which it will been reported in the SystemVnVReport.}

\wss{Use ``uses'' to
  get the correct opening and closing quotes.}\aida{Thanks! Fixed throughout the document.}

\subsubsection{Output Tests} \label{TC_ValidOutFS} 

\paragraph{Test Derived Values} 
~\newline \noindent The following set of test cases are intended to 
verify initial inputs have been correctly converted into derived
quantities. These test cases follow term definitions and equations in the Section \ref{SRS-sec_datadef} of the SRS. \wss{proof read}\aida{Done!} For each test case, one input  column references to the specified input table. Besides,The expected output has been specified for each test case and the control method for these test cases is automatic. The initial state for each is a new session. The tests will be performed as automated tests on the PyUnit.

\wss{The text is better for version control, and for reading in other editors,
  if you use a hard-wrap at 80 characters}\aida{Done!}


%Table 3: testDerivedValues
\begin{table}[h!]
\centering
\caption{TestDerivedValues}
\label{testDerivedValues}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{*{9}{|c|}}
\hline
\textbf{Test Case} & \textbf{Test Name} &  \textbf{Input Table} & \textbf{AR Expected}  & \textbf{SD Expected} & \textbf{LDF Expected} &\textbf{wTNT Expected}& \textbf{h Expected} & \textbf{GTF Expected}\\
\hline
\hline
TC\refstepcounter{testnum}\thetestnum \label{TstDrvdValsHSGlTy}  &  Table \ref{defaultInputTBL} & 1.0666666666666667 & 11.10180165558726 & 0.2696493494752911 & 10.0 & 9.02 & 2
\\ 
TC\refstepcounter{testnum}\thetestnum \label{TstDrvdValsANGlTy} & Table \ref{SmallDimensionTBL}  & 1.2 & 10.198039027185569 & 0.2696493494752911 & 10.0 & 7.42 & 1
\\
TC\refstepcounter{testnum}\thetestnum \label{TstDrvdValsFTGlTy} & Table \ref{LargeDimensionTBL} & 1.25 & 9.093404203047394 & 0.2696493494752911 & 15.0 & 9.02 & 4
\\  
\hline             

\end{tabular}
\end{adjustbox}
\end{table}



\subsection{Tests for Nonfunctional Requirements} \label{sec_NFRTests}

\subsubsection{Portability test}

\begin{enumerate}[label=TC\arabic*:,ref={\arabic*}]
	
\item [TC\refstepcounter{testnum}\thetestnum: \label{TC_Portability}] 
test-portability

Type: Manual
					
Initial State:There is a completed implementation of \progname{}
					
Input/Condition: -
					
Output/Result:-

					
How test will be performed: All unit tests will be run on all environments. Running \progname{} on Mac, Windows and
Linux operating systems has been considered to test this requirement. \wss{You can be more specific here.  My suggestion is
  that you explicitly say that all unit tests will be run on all environments.} \aida{Thanks!}
					
\end{enumerate}

\subsubsection{Reusability test}

\begin{enumerate}[label=TC\arabic*:,ref={\arabic*}]
	
\item [TC\refstepcounter{testnum}\thetestnum: \label{TC_Reusability}] 
test-reusability

Type: Manual

Initial State: There is a completed implementation of \progname{}
	
Input/Condition: -

Output/Result: An alternative version of \progname{} that uses the input code. 
All modules in the alternative version should be identical to the existing 
\progname{} modules, with the exception of the Input Module.

How test will be performed:  If only the Input Module is changed from the 
existing version, then the test passes and confidence in the reusability of 
\progname{}'s modules is increased. If other modules need to be changed, the 
test fails and the other modules must be modified to be completely reusable.
	
\end{enumerate}

\subsection{Traceability Between Test Cases and Requirements}

\noindent The purpose of the traceability matrix shown in 
Table~\ref{Table:T_trace} is to provide easy 
references on which requirements are verified by which test cases, and which 
test cases need to be updated if a requirement changes.  If a requirement is 
changed, the items in the column of that requirement that are marked
with an ``X'' may have to be modified as well. 

\begin{table}[!h]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		& \rref{SRS-Input}& \rref{SRS-KnownValues}& \rref{SRS-Verify}& \rref{SRS-R_OutputInput}& 
		\rref{SRS-R_ Comparison}& \rref{SRS-R_Output}\\
		\hline
		\tcref{TC_defultInput} - \tcref{TC_LowThicknessInput}                 
		& X& & & & &  \\ \hline
		\tcref{TC_defultInput} - \tcref{TC_LowThicknessInput}                 
		& &X & & & &  \\ \hline
		\tcref{TC_checkAPositiveTest} - \tcref{TC_ incorrectWEqUpprBndTest} 
		& & & X& & & \\ \hline
		\tcref{TC_defultInput} - \tcref{TC_LowThicknessInput}                             
		& & & &X& &   \\ \hline
		\tcref{TC_defultInput} - \tcref{TC_LowThicknessInput}                              
		& & & & &X &   \\ \hline
		\tcref{TstDrvdValsHSGlTy} - \tcref{TstDrvdValsFTGlTy}                                                
		& & & & & &X  \\ \hline
		
		\hline
	\end{tabular}
	\caption{Traceability Matrix Showing the Connections Between Requirements 
	and Test Cases}
	\label{Table:T_trace}
\end{table}

%\section{Static Verification Techniques} \label{sec_Static}
%
%Static verification of the \progname{} library implementation will performed using
%code review with Dr. Spencer Smith and my CAS 741 classmates.

\wss{You can remove this section.}\aida{Done!}

\wss{Since the system tests for GlassBR are fairly simple, you should be looking
  at incorporating additional tests in your plan.  For your program a usability
  survey would be a good addition.  We want it to be easy for users to get their
  results from GlassBR.  You could put some survey questions in your Appendix
  and introduce this idea in the main body of your plan.} \aida{ I put this section in the document, however I am not sure this questions would be appropriate or not!}

\subsection{Usability Survey Questions} \label{survey}


\begin{enumerate}
	\item Was the output delivered more quickly or more slowly than expected?
	\item Did the program accept the valid inputs?
	\item Did initial inputs have been correctly converted into derived
	quantities (\textit{AR}, \textit{SD}, \textit{LDF}, \textit{wTNT}, \textit{h}, \textit{GTF})?
	\item Were you able to install and test the program using the instructions?
	
	
\end{enumerate}

\newpage

\bibliographystyle {plainnat}
%\bibliography {../../../refs/References}

%\newpage

%\section{Appendix}
%
%This is where you can place additional information.
%
%\subsection{Symbolic Parameters}
%
%The definition of the test cases will call for SYMBOLIC\_CONSTANTS.
%Their values are defined in this section for easy maintenance.
%
%\subsection{Usability Survey Questions?}
%
%\wss{This is a section that would be appropriate for some projects.}

\end{document}