\documentclass[12pt,letterpaper]{article} \usepackage[utf8]{inputenc}
\usepackage{amsmath} \usepackage{amsfonts} \usepackage{amssymb}
\usepackage{tabularx} \usepackage{booktabs} \usepackage[left=0.8in, right=0.8in,
top=0.3in, bottom=0.5in]{geometry} \title{CAS 741: Problem Statement\\Glass
Breakage Analysis} \author{Vajiheh Motamer} \date{\today}

\input{../Comments}

\begin{document}

\maketitle

\begin{table}[hp] \caption{Revision History} \begin{center} \label{tab:}
\begin{tabular}{|c|c|c|c|} \hline \textbf{DATE} & \textbf{DEVELOPER} &
\textbf{CHANGE} & \textbf{REVISION}\\ \hline September 16, 2018 & Motamer,
Vajiheh & Initial Draft & 0\\ \hline \end{tabular} \end{center} \label{default}
\end{table}


\section{Introduction} Sometimes glass breaks in a building without any obvious
cause. When this occurs, it could be due to glass edge damage or surface damage
from handling andglazing that then weakens the glass during high winds, building
or framing system movement, vandalism or a specific type of inclusion inside the
glass.The past few years have seen several highly publicized incidents involving
window and balcony glass breaking spontaneously and falling from high-rise
buildings insome of megacities. GlassBR is a software used by structural
engineers to predict whether or not a slab of glass will be able to withstand a
given explosion without breaking.

\section{Importance} The term ‘safety glazing’ generally refers to any type of
glass engineered to reduce the potential for serious injury when it comes into
human contact. In addition to balcony glass, safety glazing are commonly
required for:\\ Sliding glass doors, Shower doors, Patio furniture, Skylights,
Oven glass, Automobile windshields.


\section{Context}

The stakeholders for this software are software tutorial makers, software
tutorial users, technical support, technical support users,group members, and
future developers. A Team will maintain it throughout the product’s lifespan.
Theconsumers will be the end-users who will consume a safe glass. The software
should run on a variety of personal desktop or laptop computers using Linux,
Windows, or MacOS for use by a broad user base.

\pagenumbering{gobble} \end{document}