\documentclass[12pt]{article}

\usepackage{graphicx}
\usepackage{paralist}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hhline}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{url}
\usepackage{hyperref}

\oddsidemargin -10mm
\evensidemargin -10mm
\textwidth 160mm
\textheight 200mm
\renewcommand\baselinestretch{1.0}

\pagestyle {plain}
\pagenumbering{arabic}

%% Comments

\usepackage{color}

\newif\ifcomments\commentstrue

\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi

\newcommand{\wss}[1]{\authornote{blue}{SS}{#1}}

\title{Discussion of Projectile Lesson: What and Why}
\author{Spencer Smith}

\begin {document}

\maketitle

I've adapted Section 12.6 (Motion of a Projectile) from the classic Hibbler text
"Engineering Mechanics Dynamnics, 10th edition". To take into account that
Section 12.6 builds on the previous sections, I've added an initial section that
simply provides a summary of the equations that were previously derived.  The
derivation of these equations is fairly similar to how they are derived in the
current Projectile example in Drasil.  I've made an effort to change the symbols
and notation to match what is currently in Drasil.

Comments have been incorporated into the text using square brackets [].

I've tried to write the parts using the simplest possible markdown.  Equations
are added using LaTeX.  To get cross-references to equations to work I had to
add the LaTeX extensions to my local installation of Jupyter.  Maybe there is a
better way to do cross-references?

For the code part, I tried to leave the variabilities in code (as opposed to in
the markdown), so that they can be changed easily.  The figure is ``hardcoded''
with specific values for the variable inputs.

\section {Discussion}


\end {document}